Verifying Fine-Grained and Lock-Free Binary Search Trees

### 2022-04-06 concurrency/intro.tex
minor corrections/comments

Our specifications use the logical atomicity introduced in the TaDA
logic \cite{tada}, in the form of \emph{atomic Hoare
triples}. Intuitively, an atomic Hoare triple $ \langle
P \rangle\,\mathbb{C}\, \langle Q \rangle$ means the program
$\mathbb{C}$ ``atomically updates'' from $P$ to $Q$. The program may
actually take multiple steps, but evey step before the atomic update
(linearization point) must preserve the assertion $P$. Meanwhile, the
concurrent environment may also update the state before the
linearization point, as long as the states satisfies $P$. The
assertion $Q$ must become true at the linearization point, then the
environment can do whatever it likes. There is no guarantee that $Q$
is still preserved when $\mathbb{C}$ returns. For example, the
specification of our \texttt{insert} operation may be explained as
follows: during the execution of \texttt{insert}, there is
always \emph{some} BST, and at some point the \texttt{insert} will
take a BST $t$, insert a value with a certain key, and then eventually
returns (meanwhile other threads may have further modified the
inserted tree).

@@

We highlights a few innovative aspects about our verification of CBST:
\begin{description}
\item [Range ghost] We abstract the BST via a pair of values
called \emph{range} which represents the lower-bound and upper-bound
of keys on each node to reason about the BST in the current
settings. We prove that range with the merging operation forms a
partial commutative monoid (PCM) so that it can be encoded in ghost
states.

>>>>

Our specifications use the logical atomicity introduced in the TaDA
logic \cite{tada}, in the form of \emph{atomic Hoare
triples}. Intuitively, an atomic Hoare triple $ \langle
P \rangle\,\mathbb{C}\, \langle Q \rangle$ means the program
$\mathbb{C}$ ``atomically updates'' from $P$ to $Q$. The program may
actually take multiple steps, but every step before the atomic update
(linearization point) must preserve the assertion $P$. Meanwhile, the
concurrent environment may also update the state before the
linearization point, as long as the states satisfies $P$. The
assertion $Q$ must become true at the linearization point, then the
environment can do whatever it likes. There is no guarantee that $Q$
is still preserved when $\mathbb{C}$ returns. For example, the
specification of our \texttt{insert} operation may be explained as
follows: during the execution of \texttt{insert}, there is
always \emph{some} BST, and at some point the \texttt{insert} will
take a BST $t$, insert a value with a certain key, and then eventually
returns (meanwhile other threads may have further modified the
inserted tree)\footnote{Maybe say what a reasonable $Q$ is and why such a spec is still useful, specifically w.r.t. the situation where one of the other threads' action following the linearization point removes the element just inserted.}.

@@

We highlight a few innovative aspects of our verification of CBST:
\begin{description}
\item [Range ghost] We abstract the BST via a pair of values
called \emph{range} which represents the lower-bound and upper-bound
of keys on each node to reason about the BST in the current
settings. We prove that range with the merging operation forms a
partial commutative monoid (PCM) so that it can be encoded in ghost
states.
